### 2015-01-17 src/analysis.Rnw
update

\subsection{Statistical tests}
To compute the actual advantage gained by each of the different strategies, we
calculated the paired t-test between the number of test cases reported by the
strategy, and that of random selection of the same number of operators as
baseline.

We also calculated the paired t-test between the number of mutants from the
full set which were killed by the test cases killing any of the mutants from
the selected mutants by mutation reduction strategy.

>>>>

\subsection{Statistical tests}
To compute the actual advantage gained by each of the different strategies, we
calculated the paired t-test between the number of test cases reported by the
strategy, and that of random selection of the same number of operators as
baseline, that is 
\[T.test\left(T_{strategy}\sim{}T_{random}\right)\]

We also calculated the paired t-test between the number of mutants from the
full set which were killed by the test cases killing any of the mutants from
the selected mutants by mutation reduction strategy. That is
\[T.test\left(k(T_{strategy})\sim{}k(T_{random})\right)\]

\begin{table*}[!ht]
<<tblttest, child='tbl.ttests.Rnw'>>=
@
%\caption*{Single Operators}
\caption {The t-test results}
\label{tbl:ttests}
\end{table*}

### 2015-01-17 src/ttests.Rnw
update

<<tests,results='asis'>>=
mintc.t.test <- function(db) {
  return(with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater"))))
}
mutant.t.test <- function(db) {
  return(with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater"))))
}
db <- subset(common.db, kind == "nsel")
nsel.t <- mintc.t.test(db)
nsel.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "opsel")
opsel.t <- mintc.t.test(db)
opsel.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "single")
single.t <- mintc.t.test(db)
single.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "opx")
opx.t <- mintc.t.test(db)
opx.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "lmcp")
lmcp.t <- mintc.t.test(db)
lmcp.m <- mutant.t.test(db)
# #---------------------------------------
# # nmc     nc       rc       dc       rv       ic       cc
# # emv      vmc      m       cb       i        ri       rs       es in
# db <- subset(common.db, operator == "rm_nmc")
# with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater")))
# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater")))
# #---------------------------------------
# db <- subset(common.db, operator == "cc")
# with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater")))
# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater")))
# #---------------------------------------
# db <- subset(common.db, operator == "clazz")
# with(db, t.test(sel.mintc,sample.mintc, paired=T)) #, alternative=c("greater")))
# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T))#, alternative=c("greater")))
@

>>>>

<<tests,results='asis'>>=
mintc.t.test <- function(db) {
  return(with(db, t.test(sel.mintc,sample.mintc, paired=T))) #, alternative=c("greater"))))
}
mutant.t.test <- function(db) {
  return(with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T))) #, alternative=c("greater"))))
}
db <- subset(common.db, kind == "nsel")
nsel.t <- mintc.t.test(db)
nsel.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "opsel")
opsel.t <- mintc.t.test(db)
opsel.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "single")
single.t <- mintc.t.test(db)
single.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "opx")
opx.t <- mintc.t.test(db)
opx.m <- mutant.t.test(db)
#-- Insufficient evidence that sel.mintc is greater than random selection
db <- subset(common.db, kind == "lmcp")
lmcp.t <- mintc.t.test(db)
lmcp.m <- mutant.t.test(db)
# #---------------------------------------
# # nmc     nc       rc       dc       rv       ic       cc
# # emv      vmc      m       cb       i        ri       rs       es in
# db <- subset(common.db, operator == "rm_nmc")
# with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater")))
# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater")))
# #---------------------------------------
# db <- subset(common.db, operator == "cc")
# with(db, t.test(sel.mintc,sample.mintc, paired=T, alternative=c("greater")))
# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T, alternative=c("greater")))
# #---------------------------------------
# db <- subset(common.db, operator == "clazz")
# with(db, t.test(sel.mintc,sample.mintc, paired=T)) #, alternative=c("greater")))
# with(db, t.test(sel.all.killtcd_mutant,sample.all.killtcd_mutant, paired=T))#, alternative=c("greater")))
db <- subset(common.db, operator=="constrained")
constrained.t <- mintc.t.test(db)
constrained.m <- mutant.t.test(db)

db <- subset(common.db, operator=="eselective")
eselective.t <- mintc.t.test(db)
eselective.m <- mutant.t.test(db)

db <- subset(common.db, operator=="javalanche")
javalanche.t <- mintc.t.test(db)
javalanche.m <- mutant.t.test(db)

db <- subset(common.db, operator=="varreduction")
variable.t <- mintc.t.test(db)
variable.m <- mutant.t.test(db)

db <- subset(common.db, operator=="sdl")
sdl.t <- mintc.t.test(db)
sdl.m <- mutant.t.test(db)

db <- subset(common.db, operator=="line")
line.t <- mintc.t.test(db)
line.m <- mutant.t.test(db)

db <- subset(common.db, operator=="method")
method.t <- mintc.t.test(db)
method.m <- mutant.t.test(db)

db <- subset(common.db, operator=="clazz")
clazz.t <- mintc.t.test(db)
clazz.m <- mutant.t.test(db)

# rm_none      rm_nmc       rm_nc        rm_rc        rm_dc        rm_rv
# rm_ic        rm_cc       rm_emv       rm_vmc       rm_m         rm_cb
# rm_i         rm_ri        rm_rs        rm_es       
db <- subset(common.db, operator=="rm_nmc")
rm.nmc.t <- mintc.t.test(db)
rm.nmc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_rv")
rm.rv.t <- mintc.t.test(db)
rm.rv.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_ic")
rm.ic.t <- mintc.t.test(db)
rm.ic.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_dc")
rm.dc.t <- mintc.t.test(db)
rm.dc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_nc")
rm.nc.t <- mintc.t.test(db)
rm.nc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_rc")
rm.rc.t <- mintc.t.test(db)
rm.rc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_vmc")
rm.vmc.t <- mintc.t.test(db)
rm.vmc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_cc")
rm.cc.t <- mintc.t.test(db)
rm.cc.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_emv")
rm.emv.t <- mintc.t.test(db)
rm.emv.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_m")
rm.m.t <- mintc.t.test(db)
rm.m.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_cb")
rm.cb.t <- mintc.t.test(db)
rm.cb.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_i")
rm.i.t <- mintc.t.test(db)
rm.i.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_ri")
rm.ri.t <- mintc.t.test(db)
rm.ri.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_rs")
rm.rs.t <- mintc.t.test(db)
rm.rs.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_es")
rm.es.t <- mintc.t.test(db)
rm.es.m <- mutant.t.test(db)

db <- subset(common.db, operator=="rm_in")
rm.in.t <- mintc.t.test(db)
rm.in.m <- mutant.t.test(db)

@
